---
title: "linreg_tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

if (!requireNamespace("bench", quietly = TRUE)) {
  install.packages("bench")
}


```

```{r setup}
library(bench)
library(linreg)
```

## Introduction

This tutorial demonstrates how to use the linear_regression for performing linear regression and analyzing its outputs. The function calculates model coefficients, residuals, R-squared values, and other statistics.


## Example: Analyzing the mtcars Dataset

The mtcars dataset contains data about various car models and their properties. Let's fit a linear regression model to predict miles per gallon (mpg) using cyl, disp, and hp as predictors.

# Performing Linear Regression

Use the linear_regression to fit the model:
```{r}
data(mtcars)
result <- linear_regression(mtcars, "mpg", c("cyl", "disp", "hp"))
result
```

## Coefficients Table

The Coefficients table shows the estimated coefficients, their standard errors, confidence intervals, t-values, and p-values:

```{r}
# Coefficients table
result$Coefficients

```

## Residuals Summary

The residuals summary provides an overview of the residuals from the model:
```{r}
# Residuals summary
result$Residuals

```

## R-squared and Adjusted R-squared

The R-squared and Adjusted R-squared values indicate how well the model explains the variability in the response variable:
```{r}
# R-squared values
cat("Multiple R-squared:", result$Multiple_R_squared, "\n")
cat("Adjusted R-squared:", result$Adjusted_R_squared, "\n")

```

## Residual Standard Error

The residual standard error gives an estimate of the variability in the residuals:
```{r}
# Residual standard error
result$Residual_standard_error

```

## F-statistic

The F-statistic tests the overall significance of the model:
```{r}
# F-statistic
result$F_statistics

```

## Example: Interpreting Results

Based on the results, you can draw conclusions about the significance of the predictors (cyl, disp, hp) and the goodness of fit of the model.

Predictors with low p-values are significant contributors to the model.
A high R-squared indicates the model explains a large proportion of the variability in mpg.

## Custom Dataset Example

You can use your own dataset with the function. Here's an example using a custom dataset:

```{r}
# Create a custom dataset
custom_data <- data.frame(
  y = c(10, 20, 15, 25, 30),
  x1 = c(1, 2, 3, 4, 5),
  x2 = c(5, 7, 6, 8, 10)  
)

custom_result <- linear_regression(custom_data, "y", c("x1", "x2"))


# View the model output
custom_result

```



